---
title: "Korova Room"
author: "Roman Yaniv"
date: "04 06 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Installing packages
```{r inst_packages, include=FALSE}
install.packages("gtrendsR", repos = "http://cran.us.r-project.org")
```

Loading packages
```{r load_packages, include=TRUE}
library(gtrendsR)
library(tidyverse)
```

Compare directors - Lynch, Tarantino, Hitchcock, Wes Anderson, Kubrick in the US
```{r directors_US, include=TRUE}
directors_us <- gtrends(c("David Lynch", "Quentin Tarantino", "Hitchcock", "Wes Anderson", "Kubrick"), geo = "US")
iot_us <- directors_us$interest_over_time
```


Interest over time after 2020 - Directors US
```{r d_2020_us, include=TRUE}
iot2020_us <- iot_us %>% filter(date > as.Date("2020-01-01"))
iot2020_us %>%
      ggplot() + geom_line(aes(x = date,
                              y = hits,
                              color = keyword)) +
  theme_minimal() +
  labs(title = "Directors in the US Comparison")
```


Compare directors - Lynch, Tarantino, Hitchcock, Wes Anderson, Kubrick in the UK
```{r directors_uk, include=TRUE}
directors_uk <- gtrends(c("David Lynch", "Quentin Tarantino", "Hitchcock", "Wes Anderson", "Kubrick"), geo = "GB")
```

Interest over time after 2020 - Directors UK
```{r d_2020_uk, include=TRUE}
iot_uk <- directors_uk$interest_over_time
iot2020_uk <- iot_uk %>% filter(date > as.Date("2020-01-01"))
iot2020_uk %>%
      ggplot() + geom_line(aes(x = date,
                              y = hits,
                              color = keyword)) +
  theme_minimal() +
  labs(title = "Directors in the UK Comparison")
```

Compare movies - Twin Peaks, Pulp Fiction, Vertigo, Moonrise Kingdom, Clockwork Orange in the US
```{r movies_us, include=TRUE}
movies_us <- gtrends(c("Twin Peaks", "Pulp Fiction", "Vertigo", "Moonrise Kingdom", "Clockwork Orange"), geo = "US")
```

Interest over time after 2020 - Movies US
```{r m_2020_us, include=TRUE}
m_iot_us <- movies_us$interest_over_time
m_iot_us$hits <- as.numeric(m_iot_us$hits)
m_iot2020_us <- m_iot_us %>% filter(date > as.Date("2020-01-01"))
m_iot2020_us %>%
      ggplot() + geom_line(aes(x = date,
                              y = hits,
                              color = keyword)) +
  theme_minimal() +
  labs(title = "Movies in the US Comparison")
```

Compare movies - Twin Peaks, Pulp Fiction, Vertigo, Moonrise Kingdom, Clockwork Orange in the UK
```{r movies_uk, include=TRUE}
movies_uk <- gtrends(c("Twin Peaks", "Pulp Fiction", "Vertigo", "Moonrise Kingdom", "Clockwork Orange"), geo = "GB")
```

Interest over time after 2020 - Movies UK
```{r m_2020_uk, include=TRUE}
m_iot_uk <- movies_uk$interest_over_time
m_iot_uk$hits <- as.numeric(m_iot_uk$hits)
m_iot2020_uk <- m_iot_uk %>% filter(date > as.Date("2020-01-01"))
m_iot2020_uk %>%
      ggplot() + geom_line(aes(x = date,
                              y = hits,
                              color = keyword)) +
  theme_minimal() +
  labs(title = "Movies in the UK Comparison")
```